Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-09-09 introduction.tex
Address reviewers' comments: please review/iterate
Introduction - addressing a reviewer comment.
  "ain't no cure for reviewers with a vendetta"..

\ifreview
Comments to address in this section:
\begin{enumerate}
	\color{red} 
	\item REVIEWER 1: The introduction is overly verbose and prosaic. The
	praise for LHC collaborations is off-putting, especially as it ignores
	other work. For example, claiming "CMS and ATLAS experiments utilize
	arguably the largest production grade distributed computing solutions"
	disregards the obvious commercial contenders. By blatantly excluding
	obvious comparisons, it raises the question how much other work is
	ignored.
\end{enumerate}
\fi

@@

The LHC workloads are comprised of tasks that are independent of each other,
however, the management of the distribution of workloads across many
heterogeneous resources, the effective utilization of resources and efficient
execution of workloads present non-trivial challenges. Many software solutions
have been developed in response to these challenges. The CMS experiment,
devised a solution based around the HTCondor~\cite{thain2005distributed}
software ecosystem. The ATLAS~\cite{Aad:2008} experiment utilizes the
Production and Distributed Analysis (PanDA) workload management
system~\cite{Maeno2011} (WMS) for distributed data processing and analysis.
The CMS and ATLAS experiments utilize, arguably the largest production grade
distributed computing solutions, and have symbolized the paradigm of {\it
high-throughput computing} (HTC), i.e., the effective execution of many
independent tasks.

In spite of the impressive scale of the ATLAS distributed computing system --
in the number of tasks executed, the number of core hours utilized, and the
number of distributed sites utilized,  demand for computing systems will soon
significantly outstrip current and projected supply.   The data volumes that
will need analyzing in LHC-Run 3 ($~\approx$ 2022) and the high-luminosity era
(Run 4) will increase by factors of 10--100 compared to the current phase (Run
2). There are multiple levels at which this problem needs to be addressed: the
utilization of emerging parallel architectures (e.g., platforms); algorithmic
and advances in analytical methods (e.g., use of Machine Learning); and the
ability to exploit different platforms (e.g., clouds and supercomputers).

>>>>

\ifreview
Comments to address in this section:
\begin{enumerate}
	\color{red} 
	\item REVIEWER 1: The introduction is overly verbose and prosaic. The
	praise for LHC collaborations is off-putting, especially as it ignores
	other work. For example, claiming "CMS and ATLAS experiments utilize
	arguably the largest production grade distributed computing solutions"
	disregards the obvious commercial contenders. By blatantly excluding
	obvious comparisons, it raises the question how much other work is
	ignored. \jhanote{Added "academic" after arguably. Any more?}
\end{enumerate}
\fi

@@

The LHC workloads are comprised of tasks that are independent of each other,
however, the management of the distribution of workloads across many
heterogeneous resources, the effective utilization of resources and efficient
execution of workloads present non-trivial challenges. Many software solutions
have been developed in response to these challenges. The CMS experiment,
devised a solution based around the HTCondor~\cite{thain2005distributed}
software ecosystem. The ATLAS~\cite{Aad:2008} experiment utilizes the
Production and Distributed Analysis (PanDA) workload management
system~\cite{Maeno2011} (WMS) for distributed data processing and analysis.
The CMS and ATLAS experiments utilize, arguably the largest academic
production grade distributed computing solutions, and have symbolized the
paradigm of {\it high-throughput computing} (HTC), i.e., the effective
execution of many independent tasks.

In spite of the impressive scale of the ATLAS distributed computing system --
in the number of tasks executed, the number of core hours utilized, and the
number of distributed sites utilized,  demand for computing systems will soon
significantly outstrip current and projected supply.   The data volumes that
will need analyzing in LHC-Run 3 ($\approx$ 2022) and the high-luminosity
era (Run 4) will increase by factors of 10--100 compared to the current phase
(Run 2). There are multiple levels at which this problem needs to be
addressed: the utilization of emerging parallel architectures (e.g.,
platforms); algorithmic and advances in analytical methods (e.g., use of
Machine Learning); and the ability to exploit different platforms (e.g.,
clouds and supercomputers).

### 2017-09-09 paper.tex
Address reviewers' comments: please review/iterate
Introduction - addressing a reviewer comment.
  "ain't no cure for reviewers with a vendetta"..

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    \item REVIEWER 1: There is a problem with capitalization in some
    reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    [13]. Reference [6] is just an author list, year and title. Should there
    be more here?
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.
    \item REVIEWER 2: the information provided is insufficient to asses in
    how far any of the presented evaluation, characterization or lessons are
    applicable outside of TITAN and PanDA Broker combined.
    \item REVIEWER 2: Several references are of poor quality. For example,
    [19] is a slide collection even though there are many papers for the
    referenced work.
    \item REVIEWER 3: Title looks too general for what amounts to the
    implementation of an adapter component in a system that is very specific
    to a single HEP experiment. (In general, title, abstract and conclusions
    seem to over-state the contributions of this paper, considering this is a
    general eScience conference and not a WLCG-specific one.)
\end{itemize}
\fi

@@

% ---------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
% ---------------------------------------------------------------------------
% \section*{Acknowledgements}\label{sec:ack}
% \input{ack}

% ---------------------------------------------------------------------------
% REFERENCES
% ---------------------------------------------------------------------------
% \newpage
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}

>>>>

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    % \item REVIEWER 1: There is a problem with capitalization in some
    % reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    % [13]. Reference [6] is just an author list, year and title. Should there
    % be more here?\mtnote{Fixed.}
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.
    \item REVIEWER 2: the information provided is insufficient to asses in
    how far any of the presented evaluation, characterization or lessons are
    applicable outside of TITAN and PanDA Broker combined.
    \item REVIEWER 2: Several references are of poor quality. For example,
    [19] is a slide collection even though there are many papers for the
    referenced work.\mtnote{Reference [19] is a technical paper.}
    \item REVIEWER 3: Title looks too general for what amounts to the
    implementation of an adapter component in a system that is very specific
    to a single HEP experiment. (In general, title, abstract and conclusions
    seem to over-state the contributions of this paper, considering this is a
    general eScience conference and not a WLCG-specific one.)
\end{itemize}
\fi

@@

% ---------------------------------------------------------------------------
% REFERENCES
% ---------------------------------------------------------------------------
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
